Dark Control:\\ A Unified Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-04-20 paper/paper.tex
more

@@

\begin{wrapfigure}{r}{.45\linewidth}
  \caption{\textbf{Reinforcement Learning in a nutshell.} At each step, given the current state of the environment,
    agent takes and action. This generates a reward and an observed state transition of the environment.}  
  \centering
  \includegraphics[width=.9\linewidth]{rl.png}
  \label{fig:rl}
\end{wrapfigure}

>>>>

\begin{wrapfigure}{r}{.4\linewidth}
  \caption{\textbf{Reinforcement Learning in a nutshell.} Given the current state of the environment,
    the agent takes an action (by following some policy). This generates a reward and an observed
    state transition of the environment. This process goes on until interrupted or a goal state is reached.}
  \centering
  \includegraphics[width=1.\linewidth]{rl.png}
  \label{fig:rl}
\end{wrapfigure}

@@
